---
title: "workit"
author: "Tatiana Voronova"
date: "2025-05-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
Sys.setlocale("LC_TIME", "English")
library(texreg)
library(tidyr)
library(dplyr)
library(stringr)
library(modelsummary)
library(readr)
library(lubridate)
library(gt)
library(purrr)
library(fixest)
library(patchwork)
library(ggplot2)
library(forecast)
library(sandwich)
library(lmtest)
library(broom)
library(stargazer)
library(scales)

```


# SET UP AND CREATE RATES

```{r set up again}

setwd("C:/r/data/final_dataset/final_region")

df <- read_csv("df.csv") %>% 
  arrange(date) %>%
  mutate(
    war = as.integer(date >= as.Date("2022-04-01")),
    time = time_length(interval(min(date), date), unit = "months"),
    shock_spring = as.integer(date >= as.Date("2022-04-01") & date <= as.Date("2022-06-01")),
    shock_winter = as.integer(date >= as.Date("2022-10-01") & date <= as.Date("2023-01-01")),
    shock_2019 = as.integer(date >= as.Date("2019-04-01") & date <= as.Date("2019-06-01")),
    shock_2020 = as.integer(date >= as.Date("2020-10-01") & date <= as.Date("2021-01-01")),
    shock_2021 = as.integer(date >= as.Date("2021-04-01") & date <= as.Date("2021-06-01")),
    shock_2022 = as.integer(date >= as.Date("2022-04-01") & date <= as.Date("2022-06-01")),
    shock_2023 = as.integer(date >= as.Date("2023-10-01") & date <= as.Date("2023-12-01")),
    month = factor(month(date, label = TRUE, abbr = TRUE))
  ) %>%
  mutate(
    across(
      c(rent_cpi, total_cpi,
        Tbilisi_CPI, Kutaisi_CPI, Batumi_CPI, Gori_CPI, Telavi_CPI, Zugdidi_CPI,
        Tbilisi_Rent, Kutaisi_Rent, Batumi_Rent, Gori_Rent, Telavi_Rent, Zugdidi_Rent),
      ~ 100 * (. - lag(.)) / lag(.),
      .names = "{.col}_rate"
    )
  ) %>%
  filter(date > as.Date("2016-01-01") & date <= as.Date("2023-12-01"))


```

### Set Up

```{r pivoting the table}

panel <- df %>%
  select(date, war, interest_rate,
         matches("^(Tbilisi|Kutaisi|Batumi|Gori|Telavi|Zugdidi)_(CPI|Rent)(_rate)?$")) %>%
  pivot_longer(
    cols = -c(date, war, interest_rate),
    names_to = c("city", "variable", "rate"),
    names_sep = "_",
    values_to = "value"
  ) %>%
  mutate(
    variable = ifelse(is.na(rate), variable, paste0(variable, "_rate"))
  ) %>%
  select(-rate) %>%
  pivot_wider(names_from = variable, values_from = value) %>%
  mutate(
    city = factor(city),
    date = as.Date(date)
  )

panel <- panel %>%
  mutate(
    time = time_length(interval(min(date), date), unit = "months"),
    shock_spring = as.integer(date >= as.Date("2022-04-01") & date <= as.Date("2022-06-01")),
    shock_winter = as.integer(date >= as.Date("2022-10-01") & date <= as.Date("2023-01-01")),
    other_cities = factor(
      if_else(city == "Tbilisi", "Tbilisi", "Other"),
      levels = c("Other", "Tbilisi")  # Set "Other" as reference
    )
  )


```


```{r making sure panel works}
cities <- panel %>%
  pull(city) %>%
  unique() %>%
  sort()

```




# ANALYSIS

## OLS


```{r NATION OLS}

m4 <- lm(rent_cpi_rate ~ war, data = df)
m5 <- lm(rent_cpi_rate ~ war + total_cpi_rate, data = df)
m6 <- lm(rent_cpi_rate ~ war + total_cpi_rate + interest_rate, data = df)

#screenreg(list(m4, m5, m6))

```



```{r CITY OLS}

# Create models and assign names manually
models_city_rates <- map(cities, function(city_name) {
  data_city <- filter(panel, city == city_name)
  lm(Rent_rate ~ war + CPI_rate + interest_rate, data = data_city)
})
names(models_city_rates) <- cities

```


```{r tbilisi vs others: city shocks}

df_tbilisi <- filter(panel, city == "Tbilisi")
df_other   <- filter(panel, city != "Tbilisi")
ols_tbilisi <- lm(Rent_rate ~ war + CPI_rate + interest_rate, data = df_tbilisi)
ols_others <- lm(Rent_rate ~ war + CPI_rate + interest_rate, data = df_other)
ols_tbilisi_shock <- lm(Rent_rate ~ time + shock_spring + shock_winter + CPI_rate + interest_rate, data = df_tbilisi)
ols_others_shock <- lm(Rent_rate ~ time + shock_spring + shock_winter + CPI_rate + interest_rate, data = df_other)

nw_se_tbilisi <- sqrt(diag(NeweyWest(ols_tbilisi, prewhite = FALSE)))
nw_se_others  <- sqrt(diag(NeweyWest(ols_others, prewhite = FALSE)))
nw_se_tbilisi_shock  <- sqrt(diag(NeweyWest(ols_tbilisi_shock, prewhite = FALSE)))
nw_se_others_shock  <- sqrt(diag(NeweyWest(ols_others_shock, prewhite = FALSE)))

screenreg(list(ols_tbilisi, ols_others, ols_tbilisi_shock, ols_others_shock))
```




## TWFE

```{r TWFE rates}
twfe_rates_model <- feols(
  Rent_rate ~ i(city, war, ref = "Tbilisi") + CPI_rate | city + date,
  cluster = ~city,
  data = panel
)
screenreg(twfe_rates_model)
```

```{r TBILISI VS OTHERS}
twfe_tbilisi_vs_other <- feols(
  Rent_rate ~ i(other_cities, war, ref = "Other") + CPI_rate | city + date,
  cluster = ~city,
  data = panel
)

screenreg(twfe_tbilisi_vs_other)
```


## Shock Analysis

```{r shock nationwide}
# Run model with both shocks
model_dual_shocks <- lm(
  rent_cpi_rate ~ time + shock_spring + shock_winter + total_cpi_rate + interest_rate,
  data = df
)

screenreg(model_dual_shocks)

```

```{r city-specific shocks}

shock_models_city <- panel %>%
  group_split(city) %>%
  setNames(unique(panel$city)) %>%
  map(~ lm(Rent_rate ~ time + shock_spring + shock_winter + CPI_rate + interest_rate, data = .x))

screenreg(shock_models_city)

```

```{r TWFE shocks}
twfe_shock_model <- feols(
  Rent_rate ~ 
    i(city, shock_spring, ref = "Tbilisi") + 
    i(city, shock_winter, ref = "Tbilisi") + 
    CPI_rate | city + date,
  cluster = ~city,
  data = panel
)

screenreg(twfe_shock_model)
```
```{r TWFE SHOCK TBILISI VS OTHERS}
twfe_shock_tbilisi_vs_other <- feols(
  Rent_rate ~ 
    i(other_cities, shock_spring, ref = "Other") + 
    i(other_cities, shock_winter, ref = "Other") + 
    CPI_rate | city + date,
  cluster = ~city,
  data = panel
)

screenreg(twfe_shock_tbilisi_vs_other)

```


# Robustness
## Seasonality and placebo

```{r seasonality checks}

# for monthly rates
season_rent_rate <- lm(rent_cpi_rate ~ month, data = df)
season_cpi_rate <- lm(total_cpi_rate ~ month, data = df)

screenreg(list(season_rent_rate, season_cpi_rate))

shock_compare_model <- lm(
  rent_cpi_rate ~ time + shock_2019 + shock_2020 + shock_2021 + shock_2022 + shock_2023 + total_cpi_rate + interest_rate,
  data = df
)

```


# VISUALS AND OUTPUT

```{r seasonality save}



# Compute Newey–West standard errors
nw_se_rent <- sqrt(diag(NeweyWest(season_rent_rate, prewhite = FALSE)))

# Save LaTeX table with Newey–West SEs (Rent only)
stargazer(
  season_rent_rate,
  se = list(nw_se_rent),
  type = "latex",
  title = "Seasonality Check: Monthly Rent Growth Rates (Newey–West SEs)",
  column.labels = "Rent Growth Rate",
  dep.var.labels = "Monthly Growth Rate",
  covariate.labels = paste("Month:", month.abb[2:12]),  # Feb–Dec, Jan is base
  intercept.bottom = TRUE,
  omit.stat = c("aic", "bic", "ll", "f", "ser"),
  star.cutoffs = c(0.05, 0.01, 0.001),
  digits = 2,
  out = "seasonality_rent_inflation_rates.tex"
)


```


## Visual for rent cumulative and monthly inflation rent

```{r}

# Plot 1: Rent index over time
p1 <- ggplot(df, aes(x = date, y = rent_cpi)) +
  geom_line(color = "steelblue", size = 1) +
  labs(
    title = "",
    x = "Date",
    y = "Rent CPI Index"
  ) +
  theme_minimal()

# Plot 2: Monthly rent inflation (% change)
p2 <- ggplot(df, aes(x = date, y = rent_cpi_rate)) +
  geom_line(color = "firebrick", size = 1) +
  geom_vline(xintercept = as.Date("2022-03-01"), linetype = "dashed", color = "black") +
  geom_vline(xintercept = as.Date("2022-05-01"), linetype = "dashed", color = "black") +
  geom_vline(xintercept = as.Date("2022-10-01"), linetype = "dashed", color = "black") +
  geom_vline(xintercept = as.Date("2023-01-01"), linetype = "dashed", color = "black") +
  labs(
    title = "",
    x = "",
    y = "Monthly Rent Growth Rate (%)"
  ) +
  theme_minimal()

p1
p2


# Save Plot 1
ggsave("p1.png", plot = p1, width = 8, height = 5, dpi = 300)

# Save Plot 2
ggsave("p2.png", plot = p2, width = 8, height = 5, dpi = 300)

```

## Basic OLS: cities

```{r rate}
# Get city names from model list names


vcovs_city_rates <- lapply(models_city_rates, NeweyWest, prewhite = FALSE)

stargazer(
  models_city_rates,
  type = "latex",
  title = "OLS: Rent Rate Regressions by City (Newey–West SEs)",
  se = vcovs_city_rates,
  covariate.labels = c("War", "Inflation Rate", "Interest Rate"),
  column.labels = names(models_city_rates),
  column.separate = rep(1, length(models_city_rates)),
  dep.var.labels = "Rent Growth Rate",
  omit.stat = c("aic", "bic", "ll", "f", "ser"),
  star.cutoffs = c(0.05, 0.01, 0.001),
  digits = 2,
  out = "rent_rate_city.tex"
)
```


## Parallel trends

```{r parallel trends}

# Filter data for pre-war period
prewar_data <- panel %>%
  filter(date >= as.Date("2021-01-01") & date <= as.Date("2022-02-01"))
parallel_trends <- ggplot(prewar_data, aes(x = date, y = Rent_rate)) +
  geom_line(color = "steelblue", size = 0.6) +
  facet_wrap(~ city, ncol = 3) +  # 3 columns, 6 cities = 2 rows
  labs(
    title = "",
    x = "Date",
    y = "Rent Growth Rate"
  ) +
  theme_minimal() +
  theme(
    strip.text = element_text(face = "bold"),  # bold city labels
    panel.spacing = unit(1, "lines"),           # spacing between plots
    axis.text.x = element_text(angle = 45, hjust = 1)
  )
parallel_trends
ggsave("C:/r/data/final_dataset/final_region/parallel_trends.png", plot = parallel_trends_2, width = 8, height = 6, dpi = 300)

```

## TWFE

```{r}
etable(
  twfe_rates_model,
  dict = c("city::Batumi:war" = "Batumi vs. Tbilisi",
           "city::Gori:war" = "Gori vs. Tbilisi",
           "city::Kutaisi:war" = "Kutaisi vs. Tbilisi",
           "city::Telavi:war" = "Telavi vs. Tbilisi",
           "city::Zugdidi:war" = "Zugdidi vs. Tbilisi",
           "CPI_rate" = "Inflation Rate"),
  tex = TRUE,  #
  file = "C:/r/data/final_dataset/final_region/twfe_rates.tex"
)

```


## Visualizing rents and transfers


```{r visual for rents and transfers}
# Step 1: Create log variable
df <- df %>%
  mutate(log_transfers_rus = log(transfers_rus))

# Step 2: Get scaling parameters
range_rent <- range(df$rent_cpi, na.rm = TRUE)
range_log <- range(df$log_transfers_rus, na.rm = TRUE)

# Manual scaling
scale_factor <- diff(range_rent) / diff(range_log)
offset <- range_rent[1] - range_log[1] * scale_factor

# Step 3: Plot
rent_transfers <- ggplot(df, aes(x = date)) +
  geom_line(aes(y = rent_cpi, color = "Rent CPI"), size = 1) +
  geom_line(aes(y = log_transfers_rus * scale_factor + offset, color = "Log(Transfers from Russia)"), 
            size = 1, linetype = "dashed") +
  scale_y_continuous(
    name = "Rent CPI",
    sec.axis = sec_axis(
      trans = ~ (. - offset) / scale_factor,
      name = "Log(Transfers from Russia)"
    )
  ) +
  scale_color_manual(values = c("Rent CPI" = "blue", "Log(Transfers from Russia)" = "red")) +
  labs(
    title = "",
    x = "Date",
    color = "Variable"
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.title.y.left = element_text(color = "blue"),
    axis.title.y.right = element_text(color = "red")
  )


ggsave("C:/r/data/final_dataset/final_region/rents_transfers.png", plot = rent_transfers, width = 8, height = 6, dpi = 300)

```


```{r money tranfers}

# Filter data from 2019 onward
df_filtered <- df %>% 
  filter(date >= as.Date("2019-01-01"))

# Base plot with vertical dashed lines
p <- ggplot(df_filtered, aes(x = date, y = transfers_rus)) +
  geom_line(color = "black", size = 1) +
  
  # Vertical lines marking migration wave periods
  geom_vline(xintercept = as.Date("2022-04-01"), linetype = "dashed", color = "black") +
  geom_vline(xintercept = as.Date("2022-06-30"), linetype = "dashed", color = "black") +
  geom_vline(xintercept = as.Date("2022-10-01"), linetype = "dashed", color = "black") +
  geom_vline(xintercept = as.Date("2023-01-01"), linetype = "dashed", color = "black") +

  scale_y_continuous(
    labels = comma_format(accuracy = 1),
    limits = c(0, NA)
  ) +
  
  labs(
    title = "Money Transfers from Russia (2019–2023)",
    x = "Date",
    y = "Transfers (Thousand USD)"
  ) +
  
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    axis.text.y = element_text(angle = 0)
  )


# Save the plot
ggsave("money_transfers.png", plot = p, width = 8, height = 5, dpi = 300)

```


### saving city-specific shocks
```{r}
# Newey–West SEs for each city-specific shock model
se_shock_models_city <- lapply(shock_models_city, function(model) {
  sqrt(diag(NeweyWest(model, prewhite = FALSE)))
})
# Extract city names
shock_city_names <- names(shock_models_city)

# Stargazer table
stargazer(
  shock_models_city,
  type = "latex",
  title = "OLS: City-Level Effects of War Shocks on Rent Inflation (Newey–West SEs)",
  se = se_shock_models_city,
  covariate.labels = c("Time", "Spring Shock", "Winter Shock", "Inflation Rate", "Interest Rate"),
  column.labels = shock_city_names,
  column.separate = rep(1, length(shock_models_city)),
  dep.var.labels = "Rent Growth Rate",
  intercept.bottom = TRUE,
  omit.stat = c("aic", "bic", "ll", "f", "ser"),
  star.cutoffs = c(0.05, 0.01, 0.001),
  digits = 2,
  out = "shock_city_rent.tex"
)

```


### twfe shock model and save
```{r twfe shock}

# Save etable for TWFE shock model to LaTeX
fixest::etable(
  twfe_shock_model,
  tex = TRUE,
  file = "C:/r/data/final_dataset/final_region/twfe_shock_model.tex",
  title = "TWFE: Shock Effects on Rent Growth (vs. Tbilisi)",
  dict = c(
    "city::Batumi:shock_spring"  = "Batumi – Spring Shock",
    "city::Gori:shock_spring"    = "Gori – Spring Shock",
    "city::Kutaisi:shock_spring" = "Kutaisi – Spring Shock",
    "city::Telavi:shock_spring"  = "Telavi – Spring Shock",
    "city::Zugdidi:shock_spring" = "Zugdidi – Spring Shock",
    "city::Batumi:shock_winter"  = "Batumi – Winter Shock",
    "city::Gori:shock_winter"    = "Gori – Winter Shock",
    "city::Kutaisi:shock_winter" = "Kutaisi – Winter Shock",
    "city::Telavi:shock_winter"  = "Telavi – Winter Shock",
    "city::Zugdidi:shock_winter" = "Zugdidi – Winter Shock",
    "CPI_rate"                   = "Inflation Rate"
  )
)

```


## Placebo save
```{r}


## 1. One-model list ------------------------------------------------------
models_placebo <- list(shock_compare_model)

## 2. Newey-West SE vector -----------------------------------------------
nw_se_placebo <- list(sqrt(diag(NeweyWest(shock_compare_model, prewhite = FALSE))))

## 3. Stargazer -----------------------------------------------------------
stargazer(
  models_placebo,
  type  = "latex",
  se    = nw_se_placebo,
  float = FALSE,
  title = "Placebo Model: Rent Growth During Random Shock Periods (Newey–West SEs)",
  label = "tab:placebo_rent",                 # reference name
  dep.var.labels = "Rent Growth Rate",

  # keep coefficients in the order you want
  order = c("time",
            "shock_2019","shock_2020","shock_2021",
            "shock_2022","shock_2023",
            "total_cpi_rate","interest_rate"),

  covariate.labels = c("Time",
                       "Shock 2019 (Mar–May)",
                       "Shock 2020 (Oct–Jan)",
                       "Shock 2021 (Mar–May)",
                       "Shock 2022 (Mar–May)",
                       "Shock 2023 (Oct–Dec)",
                       "Inflation Rate","Interest Rate"),

  intercept.bottom = TRUE,                    # constant stays last
  omit.stat        = c("aic","bic","ll","f","ser"),
  star.cutoffs     = c(.05,.01,.001),
  digits           = 2,
  out              = "placebo_model_nw.tex"    # write the file
)

```



## OLS Nationwide
```{r saving basic ols nationwide}

## 1. models 
models_rates <- list(m4, m5, m6)

## 2. Newey-West SE vectors 
nw_se <- lapply(models_rates, \(m) sqrt(diag(NeweyWest(m, prewhite = FALSE))))

stargazer(
  models_rates,
  type  = "latex",
  se    = nw_se,
  float = FALSE,
  title = "OLS Results: Monthly Rent Growth and the War, Nationwide (Newey-West SEs)",
  dep.var.labels = "Rent Growth Rate",

  ## tell stargazer which coefficients (and in what order) to print
  order            = c("war", "total_cpi_rate", "interest_rate"),

  ## now give exactly the same number of labels
  covariate.labels = c("War", "Inflation Rate", "Interest Rate"),

  intercept.bottom = TRUE,          # constant stays at the bottom
  omit.stat        = c("aic","bic","ll","f","ser"),
  star.cutoffs     = c(.05,.01,.001),
  digits           = 2,
  out              = "rent_rate_ols_nation.tex"
)


```

```{r nation shock}
stargazer(
  model_dual_shocks,
  type   = "latex",
  se     = list(sqrt(diag(NeweyWest(model_dual_shocks, prewhite = FALSE)))),
  float  = FALSE,
  title  = "Nationwide Rent Growth: Spring- and Winter-Shock Effects (Newey–West SEs)",
  label  = "tab:nation_shock",
  digits = 2,
  out    = "nation_shock.tex",

  # Rename independent variables
  covariate.labels = c(
    "Time",
    "Spring Shock",
    "Winter Shock",
    "Inflation",
    "Interest Rate"
  ),
  order = c("time", "shock_spring", "shock_winter", "total_cpi_rate", "interest_rate"),

  # Rename dependent variable
  dep.var.labels = "Rent",

  intercept.bottom = TRUE,
  omit.stat        = c("aic", "bic", "ll", "f", "ser"),
  star.cutoffs     = c(0.05, 0.01, 0.001)
)


```

```{r}
# 1. List of all models: baseline + shock model
models_all <- list(m4, m5, m6, model_dual_shocks)

# 2. List of Newey-West SEs for each model
se_all <- lapply(models_all, \(m) sqrt(diag(sandwich::NeweyWest(m, prewhite = FALSE))))

# 3. Stargazer combined output
stargazer(
  models_all,
  type  = "latex",
  se    = se_all,
  title = "OLS Results: Rent Growth, War and Migration Shocks (Newey–West SEs)",
  dep.var.labels = "Rent Growth Rate",

  # Order of coefficients
  order = c("war", "total_cpi_rate", "interest_rate", "time", "shock_spring", "shock_winter"),

  # Labels for coefficients
  covariate.labels = c(
    "War",
    "Inflation Rate",
    "Interest Rate",
    "Time",
    "Spring Shock",
    "Winter Shock"
  ),

  intercept.bottom = TRUE,
  omit.stat = c("aic", "bic", "ll", "f", "ser"),
  star.cutoffs = c(0.05, 0.01, 0.001),
  digits = 2,
  out = "combined_rent_ols.tex"
)

```
# Saving Tbilisi vs Others


```{r ols and shocks}
stargazer(
  list(ols_tbilisi, ols_others, ols_tbilisi_shock, ols_others_shock),
  type  = "latex",
  title = "OLS: Rent Growth – Tbilisi vs. Other Cities (War and Shock Effects)",
  se    = list(nw_se_tbilisi, nw_se_others, nw_se_tbilisi_shock, nw_se_others_shock),
  dep.var.labels = "Rent Growth Rate",
  column.labels  = c("Tbilisi – War", "Other – War", "Tbilisi – Shocks", "Other – Shocks"),
  covariate.labels = c(
    "War",
    "Inflation Rate",
    "Interest Rate",
    "Time",
    "Spring Shock",
    "Winter Shock"
  ),
  order = c("war", "spring_shock", "winter_shock", "CPI_rate", "interest_rate"),
  intercept.bottom = TRUE,
  omit.stat = c("aic", "bic", "ll", "f", "ser"),
  star.cutoffs = c(0.05, 0.01, 0.001),
  digits = 2,
  out = "ols_tbilisi_vs_others_combined.tex"
)

```


```{r twfe and shocks}

fixest::etable(
  list(
    "TWFE – War"   = twfe_tbilisi_vs_other,
    "TWFE – Shocks" = twfe_shock_tbilisi_vs_other
  ),
  tex = TRUE,
  file = "C:/r/data/final_dataset/final_region/twfe_tbilisi_vs_others.tex",
  title = "",
  dict = c(
    "other_cities::Tbilisi:war"          = "War",
    "other_cities::Tbilisi:shock_spring" = "Spring Shock",
    "other_cities::Tbilisi:shock_winter" = "Winter Shock",
    "CPI_rate"                         = "Inflation Rate",
    "interest_rate"                    = "Interest Rate"
  ),
  digits = 2
)


```









# DW Test

```{r}
rent_rates_models <- models_city_rates


# Define user-friendly variable names
variable_labels <- c(
  "war" = "War",
  "CPI_rate" = "Inflation Rate",
  "total_cpi_rate" = "Inflation Rate",
  "interest_rate" = "Interest Rate"
)

# -------------------------------
# ---- NATIONAL MODELS ----
# -------------------------------

# List your national models
national_models <- list("Model 1" = m4, "Model 2" = m5, "Model 3" = m6)

# Run Durbin–Watson tests on each model
dw_national <- map(national_models, dwtest)

# Combine model output and DW results into one tidy table
tidy_national <- map2_df(national_models, names(national_models), ~ {
  tidy(.x) %>%
    filter(term != "(Intercept)") %>%
    mutate(
      term = recode(term, !!!variable_labels),
      model = .y,
      dw_statistic = round(dw_national[[.y]]$statistic, 3),
      dw_p_value = round(dw_national[[.y]]$p.value, 3)
    )
}, .id = "model_id")

# Build and save national-level GT table
national_table <- tidy_national %>%
  select(model, term, estimate, std.error, p.value, dw_statistic, dw_p_value) %>%
  mutate(across(where(is.numeric), round, 3)) %>%
  gt() %>%
  cols_label(
    model = "Model",
    term = "Variable",
    estimate = "Estimate",
    std.error = "Std. Error",
    p.value = "P-Value",
    dw_statistic = "DW Statistic",
    dw_p_value = "DW P-Value"
  ) %>%
  tab_header(
    title = ""
  )

gtsave(national_table, "C:/r/data/final_dataset/final_region/dw_rents_nation.png")

# ----------------------------
# ---- CITY-LEVEL MODELS ----
# ----------------------------

# List of city-level models (must be named!)
# Example: rent_rates_models <- list(Batumi = model1, Tbilisi = model2, ...)
dw_city <- map(rent_rates_models, dwtest)

# Tidy city models and attach DW stats
tidy_city <- map_df(rent_rates_models, tidy, .id = "city") %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = recode(term, !!!variable_labels),
    dw_statistic = map_dbl(city, ~ round(dw_city[[.x]]$statistic, 3)),
    dw_p_value = map_dbl(city, ~ round(dw_city[[.x]]$p.value, 3))
  )

# Build and save city-level GT table
city_table <- tidy_city %>%
  select(city, term, estimate, std.error, p.value, dw_statistic, dw_p_value) %>%
  mutate(across(where(is.numeric), round, 3)) %>%
  gt() %>%
  cols_label(
    city = "City",
    term = "Variable",
    estimate = "Estimate",
    std.error = "Std. Error",
    p.value = "P-Value",
    dw_statistic = "DW Statistic",
    dw_p_value = "DW P-Value"
  ) %>%
  tab_header(
    title = ""
  )

gtsave(city_table, "C:/r/data/final_dataset/final_region/city_dw_table.png")

```
